---
title: "DAG and Simulation"
author: "Natalia Fedorova"
date: "2/5/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This document exists to trace the planning stages of the UB case study. The procedure is first developing the causal model and then describing this with the help of a DAG. The DAG helps make explicit direct, causal, and conditional relationships between variables and thus can inform our data analysis and help with data collection prioritization. 


Initialization
```{r}
# install.packages("dagitty")
library(dagitty)

# install.packages(c("devtools","mvtnorm","loo","coda"),dependencies=TRUE)
# library(devtools)
# install_github("rmcelreath/rethinking",ref="Experimental")

# install.packages("rethinking")
library(rethinking)
```


The DAG
```{r}
ub_dag <- dagitty( "dag {
          wealth -> loc
          wealth -> land_own
          wealth -> house_invst
          land_own -> house_invst
          soc_cap -> res_length
          res_length <-> land_own
          res_length -> intend_stay
          intend_stay -> house_invst
          intend_stay <-> land_own
          house_invst -> house_type
}")

coordinates(ub_dag) <- list( x = c(wealth = 0, loc = 1, land_own = 1, house_invst = 1, house_type = 1, soc_cap = 2, res_length = 2, intend_stay = 2),
                             y = c(wealth = 1, loc = 1, soc_cap = 1, land_own = 2, res_length = 2, intend_stay = 3, house_invst = 4, house_type = 5))

plot(ub_dag)


impliedConditionalIndependencies(ub_dag)

adjustmentSets(ub_dag, exposure = "wealth", outcome = "house_invst", type = "all")
```

Part of figuring out the DAG is writing out the functional relationships between variables:
wealth is independent from everything
location is a function of wealth and social capital
social capital is independent from everything
land ownership is a function of wealth and residence length
residence length is a function of social capital and land ownership
intended stay is a function of land ownership and residence length
house investment is a function of wealth, land ownership, and intended stay
house type is a function of house investment (and residence length maybe?)

Mediation in the DAG

An important mediation is postulated in relation to land ownership. Residence length has a direct and strong effect on land ownership, because the cost of land is not prohibitive, so given enough time even poorer people can establish ownership. On the flip side, being a new arrival preculed you from land ownership no matter how rich you are. As such, the effect of wealth is mediated by residence length. On the other hand, intended stay is mediated by wealth. Wanted to stay longterm has a positive impact on land ownership only if the person has enough resources to buy property. This must be written into the simulation process though parameter dependence - the strength of wealth is dependent on residence length, and the strength of intended stay is dependent on wealth. 



The Variables

wealth: continous, measured as monthly income (rounded), it is quite low, let's take UB's average salary in the mean (although this isn't really right). Important point is that this is wealth AT dwelling construction (which could be some years back), so it is more like past wealth
location: gps coordinate, but actually measured as distance from center in km (appropriate distribution?)
social capital: kin in UB, binary
land ownership: categorical, yes, no, ownded by kin
residence length: measured in months, since the ger districts are not that old this should be rnorm around 15 years, let's say
intended stay: measured in months (?or should we do this in categories?) 
house investment: continous, sum of upfront cost + annual upkeep * years lived
house type: categorical, ger, bashin, house (remember this is only a feature of primary residence atm)


The simulation 

```{r}
# Functions ####
get_preference_for_migrant <- function(capital, intend_stay) {
  # This function decided a migrants preference between staying with family, or squatting a empty plot 
  # based on their capital and intended stay
  # preferences are symmetrical - 2 options are very likely, and in 2 options preferences are weak
  # param capital: is both wealth and general ability of agents to get things done
  # param intend_stay: is how long agents intend to stay in environment
  # return: either "family" or "squat"
  
  if (capital > 0 && intend_stay > 0) {
    if (rbinom(1, 1, prob = 0.99) == 1) {
      return("squat")
    }
    else {
      return("family")
    }
  }
  if (capital > 0 && intend_stay <= 0) {
    if (rbinom(1, 1, prob = 0.50) == 1) {
      return("squat")
    }
    else {
      return("family")
    }
  }
  if (capital <= 0 && intend_stay > 0) {
    if (rbinom(1, 1, prob = 0.50) == 1) {
      return("squat")
    }
    else {
      return("family")
    }
  }
  if (capital <= 0 && intend_stay <= 0) {
    if (rbinom(1, 1, prob = 0.01) == 1) {
      return("squat")
    }
    else {
      return("family")
    }
  }
}

get_destination_family <- function(my_fam_id, plot_ids, plot_pop, plot_capacity, hh_df){
  # This function gets the destination (index of plot) of agent's family member where the plot is not at full capacity
  # param my_fam_id: agents family id, taken from hh_df
  # param plot_ids: matrix of plots containing hh ids
  # param plot_pop: vector containing plot population size
  # param plot_capacity: capacity of plot, max value of agents allowed
  # param hh_df: dataframe containing agent info
  # return: index of plot, or 0 if no plots free or no family available
  
  # get hh_ids of all those that are in my family
  my_fam <- subset(hh_df$hh_id, hh_df$fam_id == my_fam_id)
  
  # get index of plots where these family members live
  fam_destinations <- which(plot_ids %in% my_fam)

  # check if family plot is under capacity, if yes, move there, otherwise destination = 0 
  if ( length(fam_destinations)>0 ) {
    fam_dest_indices <- which(plot_pop[fam_destinations] < plot_capacity )
    if (length(fam_dest_indices) > 0) {
      if (length(fam_dest_indices) == 1)
        return(fam_destinations[fam_dest_indices])
      else
        return(sample(fam_destinations[fam_dest_indices], size=1))
    }
  }
  return(0)
}
  
get_destination_squat <- function(plot_pop) {
  # This function gets the destination (index of plot) of empty plot
  # squatting is a stochastic process; even if land is free, you might not find it
  # param plot_pop: vector containing plot population size
  # return: index of plot, or 0 if no plots free
  
  empty_destinations <- which(plot_pop == 0)
  if (length(empty_destinations) > 0) {
    
    # chance of finding land, even when it is available
    if(rbinom(1, 1, 0.7) == 1){
      
      if (length(empty_destinations) == 1)
        return(empty_destinations)
      else
        return(sample(empty_destinations, size=1))
    }
  }
  return(0)
}

finding_land <- function(hh_index, hh_df, plot_ids, plot_pop, plot_capacity){
  # This function carries out the land finding part of the simulation
  # based on preferences derived from capital and intended stay
  # agents either first try family, or first try to squat
  # param hh_index: index of the hh_ids under question
  # param hh_df: dataframe of household info
  # param plot_ids: matrix of plots
  # param plot_pop: vector of plot populations
  # param plot_capacity: max plot capacity
  # return: hh_df, plot_ids, plot_pop
  
  destination <- 0
  # preference dictates order of choice between empty or family plot
  preference_of_stay <- get_preference_for_migrant(hh_df$capital[hh_index], hh_df$intend_stay[hh_index])
  
  if (preference_of_stay == "family") {
    destination <- get_destination_family( hh_df$fam_id[hh_index], plot_ids, plot_pop, plot_capacity, hh_df)
    if ( destination==0 ) {
      destination <- get_destination_squat(plot_pop)
    }
  }
  else { # (preference_of_stay == "squat") 
    destination <- get_destination_squat(plot_pop)
    if(destination==0){
      destination <- get_destination_family(hh_df$fam_id[hh_index], plot_ids, plot_pop, plot_capacity, hh_df)
    }
  }
  
  # occupy!
  if ( destination > 0 ) {
    plot_pop[destination] <- plot_pop[destination] + 1
    if ( plot_pop[destination] > plot_capacity ) {
      print("##### THIS SHOULD NEVER HAPPEN! #####")
      print((plot_ids))
      print(destination)
      print(hh_df$hh_id[hh_index])
      print(plot_pop)
      print(hh_df)
    }
    plot_ids[destination , plot_pop[destination]] <- hh_df$hh_id[hh_index]
    
    # update total mig
    hh_df$total_mig[hh_index] <- hh_df$total_mig[hh_index] + 1
    
    # update hh_df to show which agents are now in the environment/occupying plots
    hh_df$in_env[hh_index] <- 1
  }
  else {
    # remove them from environment, can never come back, they ded
    hh_df$in_env[hh_index] <- 0
    
    # update total mig
    hh_df$total_mig[hh_index] <- hh_df$total_mig[hh_index] + 1
    
    print(c("The possible plots are full for id: ", hh_df$hh_id[hh_index]))
  }
  return(
    list(
      hh_df = hh_df,
      plot_ids = plot_ids,
      plot_pop = plot_pop
    )
  )
}

sim_ub <- function( tmax=10, N_plots=100, N_migrants=20, plot_capacity=2, N_fams=20) {
  # Master function for ABM
  # param tmax: number of runs
  # param N_plots: number of plots in environment
  # param N_migrants: number of agents entering environment at each timestep
  # param plot_capacity: number of agents that can stay at each plot
  # param N_fams: number of families in environment
  # return: details of the environment after simulation runs
  
  # init ####
  # init agents
  N_hh <- tmax*N_migrants
  
  hh_id <- 1:N_hh
  fam_id <- sample( 1:N_fams , size=N_hh, replace = TRUE)
  capital <- rnorm(N_hh)
  intend_stay <- rnorm(N_hh)
  residence_length_plot <- rep(0, times = N_hh)
  residence_length_total <- rep(0, times = N_hh)
  in_env <- rep(0, times = N_hh)
  house_invest <- rep(NA, times = N_hh)
  total_mig <- rep(0, times = N_hh)
  
  hh_df <- data.frame(hh_id, fam_id, capital, intend_stay, residence_length_plot, residence_length_total, total_mig, in_env, house_invest)
  
  # init plots
  plot_pop <- rep( 0 , N_plots )
  plot_own <- rep( 0 , N_plots )
  plot_house <- rep( 0 , N_plots )
  plot_ids <- matrix( 0 , nrow=N_plots , ncol=plot_capacity ) #matrix of plots to be filled with hh ids, plot_id index works as plot id
  
  #####
  
  # Timestep loop ####
  for (t in 1:tmax){
    print(c("Iteration ", t))
    
    # internal migration ####
    # find squatters (and fam on their plot), relocate
    # find plots of squatters
    squatter_plot_index <- which(plot_ids[,1] > 0 & plot_own == 0)
    
    if(length(squatter_plot_index) > 0){
      # get squatter and fam ID so they can move later
      squatter_id <- c(plot_ids[squatter_plot_index], plot_ids[,2][squatter_plot_index])
      
      #remove 0s from squatter_ids
      squatter_id <- squatter_id[squatter_id != 0]
      
      # remove squatters from plots and update plot ids
      plot_ids[squatter_plot_index] <- 0
      
      # and family
      plot_ids[,2][squatter_plot_index] <- 0
      
      # update plot_pop
      plot_pop[squatter_plot_index] <- 0
      
      # update residence length plot
      hh_df$residence_length_plot[squatter_id] <- 0
      
      # internal migration for newly displaced squatters 
      # internal migrants get first choice on migration given their premium knowledge of the environment
      for (i in 1:length(squatter_id)){
        hh_index = squatter_id[i] # one agent
        
        l <- finding_land(hh_index, hh_df, plot_ids, plot_pop, plot_capacity)
        hh_df <- l[["hh_df"]]
        plot_ids <- l[["plot_ids"]]
        plot_pop <- l[["plot_pop"]]
      }
    }
    ##### 
    
    # people staying with family reevaluate their choices ####
    # if environment has been good, they try to look for land
    # if capital is above 0, try to find empty plot
    
    # get people living with family
    visitor_plots <- which(plot_ids[,2] != 0)
    visitor_ids <- plot_ids[,2][visitor_plots]
    
    if(length(visitor_ids) > 0 ){
      for(i in 1:length(visitor_ids)){
        if(hh_df$capital[visitor_ids[i]] > 0){
          if(rbinom(1, 1, 0.7) == 1){ #stochastic
            destination <- get_destination_squat(plot_pop)
            if ( destination > 0 ) {
              # if they have found a new plot, remove them from all prior 
              plot_ids[,2][visitor_plots[i]] <- 0
              plot_pop[visitor_plots[i]] <- plot_pop[visitor_plots[i]] - 1
              hh_df$residence_length_plot[visitor_ids[i]] <- 0
              
              
              #put them in new plot & update total mig
              plot_pop[destination] <- plot_pop[destination] + 1
              plot_ids[destination] <- hh_df$hh_id[visitor_ids[i]]
              hh_df$total_mig[visitor_ids[i]] <-  hh_df$total_mig[visitor_ids[i]] + 1
            }
          }
        }
      }
    }
    #####
    
    # inmigration of new migrants ####
    # finding land
    for (i in 1:N_migrants){
      #calculate index so household data.frame can be indexed
      hh_index <- (t-1)*N_migrants + i #one agent
      
      l <- finding_land(hh_index, hh_df, plot_ids, plot_pop, plot_capacity)
      hh_df <- l[["hh_df"]]
      plot_ids <- l[["plot_ids"]]
      plot_pop <- l[["plot_pop"]]
    }
    #####
    
    # buying land ####
    # if live on available land from previous round, and have sufficient capital - buy land
    for (i in 1:nrow(plot_ids)){
      # get own occupied patches
      if(plot_ids[i,1] > 0){
        # if their capital is more than 0, they can buy the land (stochastic)
        if(hh_df$capital[plot_ids[i,1]] > 0 & plot_own[i] == 0){
          plot_own[i] <- rbinom(1, 1, 0.7) #stochastic
        }
      }
    }
    ##### 
    
    # building home ####
    # if live on family land stay in ger, so ignore
    # if live on own land, can build
    # investment proportional to capital and intended stay
    # min capital needed for building house: 0 
    for (i in 1:length(plot_own)){
      if(plot_own[i] == 1){
        
        if(plot_house[i] == 0){
          plot_house[i] <- rbinom(1, 1, 0.7)
          
          if(plot_house[i] == 1){
            hh_df$house_invest[plot_ids[i,1]] <- rnorm(1, hh_df$capital[plot_ids[i,1]] + hh_df$intend_stay[plot_ids[i,1]] )
          }
        }
      }
    }
    ##### 
    
    #index of agents that are in the environment
    hh_present <- which(hh_df$in_env == 1)
    
    # update residence time ####
    # for agents that are in the environment, residence +1
    for (i in 1:length(hh_present)){
      hh_df$residence_length_total[hh_present][i] <- hh_df$residence_length_total[hh_present][i] + 1
      
      # update plot residence length
      hh_df$residence_length_plot[hh_present][i] <- hh_df$residence_length_plot[hh_present][i] + 1
    }
    #####
    
    # stochastic shock to capital ####
    # city life is a lottery
    for (i in 1:length(hh_present)){
      hh_df$capital[hh_present][i] <- hh_df$capital[hh_present][i] + rnorm(1, 0, 0.25) 
    }
    #####
  }#t
  
  return(
    list(
      plot_own = plot_own,
      plot_house = plot_house, 
      ids = plot_ids,
      hh_df = hh_df
    )
  )
  
}

s <- sim_ub(tmax=10,N_plots=100)

df <- s[["hh_df"]]

# TODO 
# agents can be squatters and visitors in one timestep
# should land buying also be affected by intended stay?
# atm shocks to capital are the same for everyone, but realistically shouldn't be
# track plot id in hh_df because it is a clustering variable
# have a look at the house_invest stuff because it is giving rise to a very narrow distribution

```

Planning the analysis

Below is a walk through of relevant parts of rethinking v2 - as a learning exercise with my simulated data. 

Outcome variable would be house investment (I) so lets model that first
I ~ Normal(mu, sigma): likelihood
mu ~ Normal(0, 1): mu prior - needs to be positive, but need to think about standardizing, also need to think about how I'm making this in the abm 
sigma ~ Uniform (0, 10)
```{r}
# plot prior

# mu
# determines spread of mean
curve(dnorm(x, 0, 1), from = -10, to = 10) #normal, not a lot of spread, need to understand interpretation

# above is assuming some sort of standardization - what if we had it in euro?
# ger could be about 800 euro
# a bashin? maybe average of 5000 
# in abm, investment in ger not tracked
curve(dnorm(x, 5000, 1000), from = 3000, to = 7000)

# sigma
# flat prior constrained to be positive
curve(dunif(x, 0, 1000), from = -10, to = 10)

# sampling from priors
n <- 10000

sample_mu <- dnorm(n, 5000, 1000)
sample_sigma <- dunif(n, 0, 1000)
prior_I <- rnorm(n, sample_mu, sample_sigma) 

# calling prior I, but in df it is house_invest, either rename or just use house_invest

dens(prior_I) # now I don't understand the x axis

# write out model
# with priors that have been adjusted (working with abm form now)

m1 <- quap(
  alist(
    house_invest ~ dnorm(mu, sigma) ,
    mu ~ dnorm(0, 1) ,
    sigma ~ dunif(0, 5)
  ), data = df
)

precis(m1)

# extract samples

post <- extract.samples(m1, n = n)
precis(post)
```
Adding a predictor: linear model

Let's focus on how wealth affects house investment, focusing just on the direct relationship
mu = a + B(xi - xbar)
```{r}
# first, because here we can only deal with those that have house_invest (i.e. those that built houses), we need to work with the subset
df_s <- df[!is.na(df$house_invest), ]


# figuring out the prior for B
# must do some prior predictive simulation

n <- 100

# already have a

a <-  rnorm(n, 0, 1)
b <- rlnorm(n, 0, 1) 

plot(NULL, xlim = range(df_s$capital), ylim = c(-10, 10))
xbar <- mean(df_s$capital)
for(i in 1:n){
  curve(a[i] + b[i]*(x-xbar), add = TRUE)
}

# it doesn't really look great

xbar <- mean(df_s$capital)

m2 <- quap(
  alist(
    house_invest ~ dnorm(mu, sigma) ,
    mu ~ a + b*(capital - xbar),
    a ~ dnorm(0, 1) ,
    b ~ dlnorm(0, 1) ,
    sigma ~ dunif(0, 5)
  ), data = df_s
)

precis(m2)

# interpreting the posterior

plot(house_invest ~ capital, data = df_s)
post <- extract.samples(m2)
a_map <- mean(post$a)
b_map <- mean(post$b)
curve(a_map + b_map*(x - xbar), add = TRUE)

# drawing uncertainty

capital_seq <- seq(from = -1, to = 3, by = 1)
mu_u <- link(m2, data = data.frame(capital = capital_seq))

mu_mean <- apply(mu_u, 2, mean)
mu_hpdi <- apply(mu_u, 2, HPDI, prob = 0.89)

plot(house_invest ~ capital, data = df_s)
lines(capital_seq, mu_mean)
shade(mu_hpdi, capital_seq)

# this thing looks like it should have a ton more uncertainty. go figure. in any case - this is for mu
```