---
title: "Area selection"
author: "Natalia Fedorova"
date: "22 October 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This file serves to document the process by which study areas within Ulaanbaatar were selected for the case study. The imperative of the selection process is to select areas that are similar demographically but vary in terms of how long inhabitants have resided there

Ulaanbaatar is divided into nine districts (D????regs): Baganuur, Bagakhangai, Bayangol, Bayanz??rkh, Chingeltei, Khan Uul, Nalaikh, Songino Khairkhan and S??khbaatar. Each district is subdivided into khoroos, of which there are 121. Khoroos are further divided into Khesegs which each have a Kheseg leader responsible for door-to-door data collection and other administrative activities (these persons tend to know all the households in their khesegs). The Khesegs are the units that will be selected, and the kheseg leaders will be hired to collect data (and ultimately also be part of focal sessions, and have data ownership).

Part one of the selection process is to visualize the population age composition of the khesegs, this is based on data from the UB statistics office:
http://ubstat.mn/JobTables.aspx

Loading data from .xlsx files and renaming columns into english
```{r}
#install.packages("readxl")
library("readxl")

col_names_bagan <- c("age", "total_t", "total_m", "total_f", "k1_t", "k1_m", "k1_f", "k2_t", "k2_m", "k2_f", "k3_t", "k3_m", "k3_f", "k4_t", "k4_m", "k4_f", "k5_t", "k5_m", "k5_f")
col_names_bagah <- c("age", "total_t", "total_m", "total_f", "k1_t", "k1_m", "k1_f", "k2_t", "k2_m", "k2_f")
col_names_bayang <- c("age", "total_t", "total_m", "total_f", "k1_t", "k1_m", "k1_f", "k2_t", "k2_m", "k2_f", "k3_t", "k3_m", "k3_f", "k4_t", "k4_m", "k4_f", "k5_t", "k5_m", "k5_f", "k6_t", "k6_m", "k6_f", "k7_t", "k7_m", "k7_f", "k8_t", "k8_m", "k8_f", "k9_t", "k9_m", "k9_f", "k10_t", "k10_m", "k10_f", "k11_t", "k11_m", "k11_f", "k12_t", "k12_m", "k12_f", "k13_t", "k13_m", "k13_f", "k14_t","k14_m", "k14_f", "k15_t", "k15_m", "k15_f", "k16_t", "k16_m", "k16_f", "k17_t", "k17_m", "k17_f", "k18_t", "k18_m", "k18_f", "k19_t", "k19_m", "k19_f", "k20_t", "k20_m", "k20_f", "k21_t", "k21_m", "k21_f", "k22_t", "k22_m", "k22_f", "k23_t", "k23_m", "k23_f" )
col_names_bayanz <- c("age", "total_t", "total_m", "total_f", "k1_t", "k1_m", "k1_f", "k2_t", "k2_m", "k2_f", "k3_t", "k3_m", "k3_f", "k4_t", "k4_m", "k4_f", "k5_t", "k5_m", "k5_f", "k6_t", "k6_m", "k6_f", "k7_t", "k7_m", "k7_f", "k8_t", "k8_m", "k8_f", "k9_t", "k9_m", "k9_f", "k10_t", "k10_m", "k10_f", "k11_t", "k11_m", "k11_f", "k12_t", "k12_m", "k12_f", "k13_t", "k13_m", "k13_f", "k14_t","k14_m", "k14_f", "k15_t", "k15_m", "k15_f", "k16_t", "k16_m", "k16_f", "k17_t", "k17_m", "k17_f", "k18_t", "k18_m", "k18_f", "k19_t", "k19_m", "k19_f", "k20_t", "k20_m", "k20_f", "k21_t", "k21_m", "k21_f", "k22_t", "k22_m", "k22_f", "k23_t", "k23_m", "k23_f", "k24_t", "k24_m", "k24_f", "k25_t", "k25_m", "k25_f", "k26_t", "k26_m", "k26_f", "k27_t", "k27_m", "k27_f", "k28_t", "k28_m", "k28_f")
col_names_nal <- c("age", "total_t", "total_m", "total_f", "k1_t", "k1_m", "k1_f", "k2_t", "k2_m", "k2_f", "k3_t", "k3_m", "k3_f", "k4_t", "k4_m", "k4_f", "k5_t", "k5_m", "k5_f", "k6_t", "k6_m", "k6_f", "k7_t", "k7_m", "k7_f")
col_names_song <- c("age", "total_t", "total_m", "total_f", "k1_t", "k1_m", "k1_f", "k2_t", "k2_m", "k2_f", "k3_t", "k3_m", "k3_f", "k4_t", "k4_m", "k4_f", "k5_t", "k5_m", "k5_f", "k6_t", "k6_m", "k6_f", "k7_t", "k7_m", "k7_f", "k8_t", "k8_m", "k8_f", "k9_t", "k9_m", "k9_f", "k10_t", "k10_m", "k10_f", "k11_t", "k11_m", "k11_f", "k12_t", "k12_m", "k12_f", "k13_t", "k13_m", "k13_f", "k14_t","k14_m", "k14_f", "k15_t", "k15_m", "k15_f", "k16_t", "k16_m", "k16_f", "k17_t", "k17_m", "k17_f", "k18_t", "k18_m", "k18_f", "k19_t", "k19_m", "k19_f", "k20_t", "k20_m", "k20_f", "k21_t", "k21_m", "k21_f", "k22_t", "k22_m", "k22_f", "k23_t", "k23_m", "k23_f", "k24_t", "k24_m", "k24_f", "k25_t", "k25_m", "k25_f", "k26_t", "k26_m", "k26_f", "k27_t", "k27_m", "k27_f", "k28_t", "k28_m", "k28_f", "k29_t", "k29_m", "k29_f", "k30_t", "k30_m", "k30_f", "k31_t", "k31_m", "k31_f", "k32_t", "k32_m", "k32_f")
col_names_suh <- c("age", "total_t", "total_m", "total_f", "k1_t", "k1_m", "k1_f", "k2_t", "k2_m", "k2_f", "k3_t", "k3_m", "k3_f", "k4_t", "k4_m", "k4_f", "k5_t", "k5_m", "k5_f", "k6_t", "k6_m", "k6_f", "k7_t", "k7_m", "k7_f", "k8_t", "k8_m", "k8_f", "k9_t", "k9_m", "k9_f", "k10_t", "k10_m", "k10_f", "k11_t", "k11_m", "k11_f", "k12_t", "k12_m", "k12_f", "k13_t", "k13_m", "k13_f", "k14_t", "k14_m", "k14_f", "k15_t", "k15_m", "k15_f", "k16_t", "k16_m", "k16_f", "k17_t", "k17_m", "k17_f", "k18_t", "k18_m", "k18_f", "k19_t", "k19_m", "k19_f", "k20_t", "k20_m", "k20_f")
col_names_han <- c("age", "total_t", "total_m", "total_f", "k1_t", "k1_m", "k1_f", "k2_t", "k2_m", "k2_f", "k3_t", "k3_m", "k3_f", "k4_t", "k4_m", "k4_f", "k5_t", "k5_m", "k5_f", "k6_t", "k6_m", "k6_f", "k7_t", "k7_m", "k7_f", "k8_t", "k8_m", "k8_f", "k9_t", "k9_m", "k9_f", "k10_t", "k10_m", "k10_f", "k11_t", "k11_m", "k11_f", "k12_t", "k12_m", "k12_f", "k13_t", "k13_m", "k13_f", "k14_t","k14_m", "k14_f", "k15_t", "k15_m", "k15_f", "k16_t", "k16_m", "k16_f")
col_names_ching <- c("age", "total_t", "total_m", "total_f", "k1_t", "k1_m", "k1_f", "k2_t", "k2_m", "k2_f", "k3_t", "k3_m", "k3_f", "k4_t", "k4_m", "k4_f", "k5_t", "k5_m", "k5_f", "k6_t", "k6_m", "k6_f", "k7_t", "k7_m", "k7_f", "k8_t", "k8_m", "k8_f", "k9_t", "k9_m", "k9_f", "k10_t", "k10_m", "k10_f", "k11_t", "k11_m", "k11_f", "k12_t", "k12_m", "k12_f", "k13_t", "k13_m", "k13_f", "k14_t", "k14_m", "k14_f", "k15_t", "k15_m", "k15_f", "k16_t", "k16_m", "k16_f", "k17_t", "k17_m", "k17_f", "k18_t", "k18_m", "k18_f", "k19_t", "k19_m", "k19_f")

#2011-2012
d_2011_baganuur <- read_xlsx("khun_amiin_too_neg_nasnii_buleg_khoroogoor_2011_on-2012.xlsx" , sheet = 1, col_names = col_names_bagan, skip = 4)
d_2011_bagahangai <- read_xlsx("khun_amiin_too_neg_nasnii_buleg_khoroogoor_2011_on-2012.xlsx" , sheet = 2, col_names = col_names_bagah, skip = 4)
d_2011_bayangol <- read_xlsx("khun_amiin_too_neg_nasnii_buleg_khoroogoor_2011_on-2012.xlsx" , sheet = 3, col_names = col_names_bayang, skip = 4)
d_2011_bayanzurkh <- read_xlsx("khun_amiin_too_neg_nasnii_buleg_khoroogoor_2011_on-2012.xlsx" , sheet = 4, col_names = col_names_bayanz, skip = 4)
d_2011_nalaih <- read_xlsx("khun_amiin_too_neg_nasnii_buleg_khoroogoor_2011_on-2012.xlsx" , sheet = 5, col_names = col_names_nal, skip = 4)
d_2011_songinohairhan <- read_xlsx("khun_amiin_too_neg_nasnii_buleg_khoroogoor_2011_on-2012.xlsx" , sheet = 6, col_names = col_names_song, skip = 4)
d_2011_suhbaatar <- read_xlsx("khun_amiin_too_neg_nasnii_buleg_khoroogoor_2011_on-2012.xlsx" , sheet = 7, col_names = col_names_suh, skip = 4)
d_2011_hanull <- read_xlsx("khun_amiin_too_neg_nasnii_buleg_khoroogoor_2011_on-2012.xlsx" , sheet = 8, col_names = col_names_han, skip = 4)
d_2011_chingeltei <- read_xlsx("khun_amiin_too_neg_nasnii_buleg_khoroogoor_2011_on-2012.xlsx" , sheet = 9, col_names = col_names_ching, skip = 4)

#2014-2015
d_2014_baganuur <- read_xlsx("khun_amiin_too_neg_nasnii_buleg_khoroogoor_2014_on-2015.xlsx" , sheet = 1, col_names = col_names_bagan, skip = 4)
d_2014_bagahangai <- read_xlsx("khun_amiin_too_neg_nasnii_buleg_khoroogoor_2014_on-2015.xlsx" , sheet = 2, col_names = col_names_bagah, skip = 4)
d_2014_bayangol <- read_xlsx("khun_amiin_too_neg_nasnii_buleg_khoroogoor_2014_on-2015.xlsx" , sheet = 3, col_names = col_names_bayang, skip = 4)
d_2014_bayanzurkh <- read_xlsx("khun_amiin_too_neg_nasnii_buleg_khoroogoor_2014_on-2015.xlsx" , sheet = 4, col_names = col_names_bayanz, skip = 4)
d_2014_nalaih <- read_xlsx("khun_amiin_too_neg_nasnii_buleg_khoroogoor_2014_on-2015.xlsx" , sheet = 5, col_names = col_names_nal, skip = 4)
d_2014_songinohairhan <- read_xlsx("khun_amiin_too_neg_nasnii_buleg_khoroogoor_2014_on-2015.xlsx" , sheet = 6, col_names = col_names_song, skip = 4)
d_2014_suhbaatar <- read_xlsx("khun_amiin_too_neg_nasnii_buleg_khoroogoor_2014_on-2015.xlsx" , sheet = 7, col_names = col_names_suh, skip = 4)
d_2014_hanull <- read_xlsx("khun_amiin_too_neg_nasnii_buleg_khoroogoor_2014_on-2015.xlsx" , sheet = 8, col_names = col_names_han, skip = 4)
d_2014_chingeltei <- read_xlsx("khun_amiin_too_neg_nasnii_buleg_khoroogoor_2014_on-2015.xlsx" , sheet = 9, col_names = col_names_ching, skip = 4)

#2015-2016
d_2015_baganuur <- read_xlsx("khun_amiin_too_neg_nasnii_buleg_khoroogoor_2015_on-2016.xlsx" , sheet = 1, col_names = col_names_bagan, skip = 4)
d_2015_bagahangai <- read_xlsx("khun_amiin_too_neg_nasnii_buleg_khoroogoor_2015_on-2016.xlsx" , sheet = 2, col_names = col_names_bagah, skip = 4)
d_2015_bayangol <- read_xlsx("khun_amiin_too_neg_nasnii_buleg_khoroogoor_2015_on-2016.xlsx" , sheet = 3, col_names = col_names_bayang, skip = 4)
d_2015_bayanzurkh <- read_xlsx("khun_amiin_too_neg_nasnii_buleg_khoroogoor_2015_on-2016.xlsx" , sheet = 4, col_names = col_names_bayanz, skip = 4)
d_2015_nalaih <- read_xlsx("khun_amiin_too_neg_nasnii_buleg_khoroogoor_2015_on-2016.xlsx" , sheet = 5, col_names = col_names_nal, skip = 4)
d_2015_songinohairhan <- read_xlsx("khun_amiin_too_neg_nasnii_buleg_khoroogoor_2015_on-2016.xlsx" , sheet = 6, col_names = col_names_song, skip = 4)
d_2015_suhbaatar <- read_xlsx("khun_amiin_too_neg_nasnii_buleg_khoroogoor_2015_on-2016.xlsx" , sheet = 7, col_names = col_names_suh, skip = 4)
d_2015_hanull <- read_xlsx("khun_amiin_too_neg_nasnii_buleg_khoroogoor_2015_on-2016.xlsx" , sheet = 8, col_names = col_names_han, skip = 4)
d_2015_chingeltei <- read_xlsx("khun_amiin_too_neg_nasnii_buleg_khoroogoor_2015_on-2016.xlsx" , sheet = 9, col_names = col_names_ching, skip = 4)

#2016-2017
d_2016_baganuur <- read_xlsx("khun_amiin_too_neg_nasnii_buleg_khoroogoor_2016_on-2017.xlsx" , sheet = 1, col_names = col_names_bagan, skip = 4)
d_2016_bagahangai <- read_xlsx("khun_amiin_too_neg_nasnii_buleg_khoroogoor_2016_on-2017.xlsx"  , sheet = 2, col_names = col_names_bagah, skip = 4)
d_2016_bayangol <- read_xlsx("khun_amiin_too_neg_nasnii_buleg_khoroogoor_2016_on-2017.xlsx" , sheet = 3, col_names = col_names_bayang, skip = 4)
d_2016_bayanzurkh <- read_xlsx("khun_amiin_too_neg_nasnii_buleg_khoroogoor_2016_on-2017.xlsx"  , sheet = 4, col_names = col_names_bayanz, skip = 4)
d_2016_nalaih <- read_xlsx("khun_amiin_too_neg_nasnii_buleg_khoroogoor_2016_on-2017.xlsx"  , sheet = 5, col_names = col_names_nal, skip = 4)
d_2016_songinohairhan <- read_xlsx("khun_amiin_too_neg_nasnii_buleg_khoroogoor_2016_on-2017.xlsx"  , sheet = 6, col_names = col_names_song, skip = 4)
d_2016_suhbaatar <- read_xlsx("khun_amiin_too_neg_nasnii_buleg_khoroogoor_2016_on-2017.xlsx"  , sheet = 7, col_names = col_names_suh, skip = 4)
d_2016_hanull <- read_xlsx("khun_amiin_too_neg_nasnii_buleg_khoroogoor_2016_on-2017.xlsx" , sheet = 8, col_names = col_names_han, skip = 4)
d_2016_chingeltei <- read_xlsx("khun_amiin_too_neg_nasnii_buleg_khoroogoor_2016_on-2017.xlsx"  , sheet = 9, col_names = col_names_ching, skip = 4)

#2017-2018
d_2017_baganuur <- read_xlsx("khun_amiin_too_neg_nasnii_buleg_khoroogoor_2017_on-2018.xlsx" , sheet = 1, col_names = col_names_bagan, skip = 4)
d_2017_bagahangai <- read_xlsx("khun_amiin_too_neg_nasnii_buleg_khoroogoor_2017_on-2018.xlsx"  , sheet = 2, col_names = col_names_bagah, skip = 4)
d_2017_bayangol <- read_xlsx("khun_amiin_too_neg_nasnii_buleg_khoroogoor_2017_on-2018.xlsx", sheet = 3, col_names = col_names_bayang, skip = 4)
d_2017_bayanzurkh <- read_xlsx("khun_amiin_too_neg_nasnii_buleg_khoroogoor_2017_on-2018.xlsx" , sheet = 4, col_names = col_names_bayanz, skip = 4)
d_2017_nalaih <- read_xlsx("khun_amiin_too_neg_nasnii_buleg_khoroogoor_2017_on-2018.xlsx", sheet = 5, col_names = col_names_nal, skip = 4)
d_2017_songinohairhan <- read_xlsx("khun_amiin_too_neg_nasnii_buleg_khoroogoor_2017_on-2018.xlsx" , sheet = 6, col_names = col_names_song, skip = 4)
d_2017_suhbaatar <- read_xlsx("khun_amiin_too_neg_nasnii_buleg_khoroogoor_2017_on-2018.xlsx"  , sheet = 7, col_names = col_names_suh, skip = 4)
d_2017_hanull <- read_xlsx("khun_amiin_too_neg_nasnii_buleg_khoroogoor_2017_on-2018.xlsx" , sheet = 8, col_names = col_names_han, skip = 4)
d_2017_chingeltei <- read_xlsx("khun_amiin_too_neg_nasnii_buleg_khoroogoor_2017_on-2018.xlsx" , sheet = 9, col_names = col_names_ching, skip = 4)

#the raw data includes summary lines (rows 6,12,18,24,30,36,42,48,54,60,66,72,78,84,90,96,102,108,114,120) which need to be removed


#want something like this: 
#city_files <- list.files('~/Documents/R/Data', pattern="USPTO_100_inventors*")
#years <- 2000:2013


years <- c(2011, 2014:2017)





d_2011_baganuur <- d_2011_baganuur[-c(6,12,18,24,30,36,42,48,54,60,66,72,78,84,90,96,102,108,114,120), ]
d_2011_bagahangai <- d_2011_bagahangai[-c(6,12,18,24,30,36,42,48,54,60,66,72,78,84,90,96,102,108,114,120), ]
d_2011_bayangol <- d_2011_bayangol[-c(6,12,18,24,30,36,42,48,54,60,66,72,78,84,90,96,102,108,114,120), ]
d_2011_bayanzurkh <- d_2011_bayanzurkh[-c(6,12,18,24,30,36,42,48,54,60,66,72,78,84,90,96,102,108,114,120), ]
d_2011_nalaih <- d_2011_nalaih[-c(6,12,18,24,30,36,42,48,54,60,66,72,78,84,90,96,102,108,114,120), ]
d_2011_songinohairhan <- d_2011_songinohairhan[-c(6,12,18,24,30,36,42,48,54,60,66,72,78,84,90,96,102,108,114,120), ]
d_2011_suhbaatar <- d_2011_suhbaatar[-c(6,12,18,24,30,36,42,48,54,60,66,72,78,84,90,96,102,108,114,120), ]
d_2011_hanull <- d_2011_hanull[-c(6,12,18,24,30,36,42,48,54,60,66,72,78,84,90,96,102,108,114,120), ]
d_2011_chingeltei <- d_2011_chingeltei[-c(6,12,18,24,30,36,42,48,54,60,66,72,78,84,90,96,102,108,114,120), ]

d_2014_baganuur <- d_2014_baganuur[-c(6,12,18,24,30,36,42,48,54,60,66,72,78,84,90,96,102,108,114,120), ]
d_2014_bagahangai <- d_2014_bagahangai[-c(6,12,18,24,30,36,42,48,54,60,66,72,78,84,90,96,102,108,114,120), ]
d_2014_bayangol <- d_2014_bayangol[-c(6,12,18,24,30,36,42,48,54,60,66,72,78,84,90,96,102,108,114,120), ]
d_2014_bayanzurkh <- d_2014_bayanzurkh[-c(6,12,18,24,30,36,42,48,54,60,66,72,78,84,90,96,102,108,114,120), ]
d_2014_nalaih <- d_2014_nalaih[-c(6,12,18,24,30,36,42,48,54,60,66,72,78,84,90,96,102,108,114,120), ]
d_2014_songinohairhan <- d_2014_songinohairhan[-c(6,12,18,24,30,36,42,48,54,60,66,72,78,84,90,96,102,108,114,120), ]
d_2014_suhbaatar <- d_2014_suhbaatar[-c(6,12,18,24,30,36,42,48,54,60,66,72,78,84,90,96,102,108,114,120), ]
d_2014_hanull <- d_2014_hanull[-c(6,12,18,24,30,36,42,48,54,60,66,72,78,84,90,96,102,108,114,120), ]
d_2014_chingeltei <- d_2014_chingeltei[-c(6,12,18,24,30,36,42,48,54,60,66,72,78,84,90,96,102,108,114,120), ]

d_2015_baganuur <- d_2015_baganuur[-c(6,12,18,24,30,36,42,48,54,60,66,72,78,84,90,96,102,108,114,120), ]
d_2015_bagahangai <- d_2015_bagahangai[-c(6,12,18,24,30,36,42,48,54,60,66,72,78,84,90,96,102,108,114,120), ]
d_2015_bayangol <- d_2015_bayangol[-c(6,12,18,24,30,36,42,48,54,60,66,72,78,84,90,96,102,108,114,120), ]
d_2015_bayanzurkh <- d_2015_bayanzurkh[-c(6,12,18,24,30,36,42,48,54,60,66,72,78,84,90,96,102,108,114,120), ]
d_2015_nalaih <- d_2015_nalaih[-c(6,12,18,24,30,36,42,48,54,60,66,72,78,84,90,96,102,108,114,120), ]
d_2015_songinohairhan <- d_2015_songinohairhan[-c(6,12,18,24,30,36,42,48,54,60,66,72,78,84,90,96,102,108,114,120), ]
d_2015_suhbaatar <- d_2015_suhbaatar[-c(6,12,18,24,30,36,42,48,54,60,66,72,78,84,90,96,102,108,114,120), ]
d_2015_hanull <- d_2015_hanull[-c(6,12,18,24,30,36,42,48,54,60,66,72,78,84,90,96,102,108,114,120), ]
d_2015_chingeltei <- d_2015_chingeltei[-c(6,12,18,24,30,36,42,48,54,60,66,72,78,84,90,96,102,108,114,120), ]

d_2016_baganuur <- d_2016_baganuur[-c(6,12,18,24,30,36,42,48,54,60,66,72,78,84,90,96,102,108,114,120), ]
d_2016_bagahangai <- d_2016_bagahangai[-c(6,12,18,24,30,36,42,48,54,60,66,72,78,84,90,96,102,108,114,120), ]
d_2016_bayangol <- d_2016_bayangol[-c(6,12,18,24,30,36,42,48,54,60,66,72,78,84,90,96,102,108,114,120), ]
d_2016_bayanzurkh <- d_2016_bayanzurkh[-c(6,12,18,24,30,36,42,48,54,60,66,72,78,84,90,96,102,108,114,120), ]
d_2016_nalaih <- d_2016_nalaih[-c(6,12,18,24,30,36,42,48,54,60,66,72,78,84,90,96,102,108,114,120), ]
d_2016_songinohairhan <- d_2016_songinohairhan[-c(6,12,18,24,30,36,42,48,54,60,66,72,78,84,90,96,102,108,114,120), ]
d_2016_suhbaatar <- d_2016_suhbaatar[-c(6,12,18,24,30,36,42,48,54,60,66,72,78,84,90,96,102,108,114,120), ]
d_2016_hanull <- d_2016_hanull[-c(6,12,18,24,30,36,42,48,54,60,66,72,78,84,90,96,102,108,114,120), ]
d_2016_chingeltei <- d_2016_chingeltei[-c(6,12,18,24,30,36,42,48,54,60,66,72,78,84,90,96,102,108,114,120), ]

d_2017_baganuur <- d_2017_baganuur[-c(6,12,18,24,30,36,42,48,54,60,66,72,78,84,90,96,102,108,114,120), ]
d_2017_bagahangai <- d_2017_bagahangai[-c(6,12,18,24,30,36,42,48,54,60,66,72,78,84,90,96,102,108,114,120), ]
d_2017_bayangol <- d_2017_bayangol[-c(6,12,18,24,30,36,42,48,54,60,66,72,78,84,90,96,102,108,114,120), ]
d_2017_bayanzurkh <- d_2017_bayanzurkh[-c(6,12,18,24,30,36,42,48,54,60,66,72,78,84,90,96,102,108,114,120), ]
d_2017_nalaih <- d_2017_nalaih[-c(6,12,18,24,30,36,42,48,54,60,66,72,78,84,90,96,102,108,114,120), ]
d_2017_songinohairhan <- d_2017_songinohairhan[-c(6,12,18,24,30,36,42,48,54,60,66,72,78,84,90,96,102,108,114,120), ]
d_2017_suhbaatar <- d_2017_suhbaatar[-c(6,12,18,24,30,36,42,48,54,60,66,72,78,84,90,96,102,108,114,120), ]
d_2017_hanull <- d_2017_hanull[-c(6,12,18,24,30,36,42,48,54,60,66,72,78,84,90,96,102,108,114,120), ]
d_2017_chingeltei <- d_2017_chingeltei[-c(6,12,18,24,30,36,42,48,54,60,66,72,78,84,90,96,102,108,114,120), ]

```
Given their spatial separation from UB, baganuur, bagahangai, and nalaikh, are not going to include study areas. For the others though, let us create plots with age structure for all the khoroos

Plotting total population by khoroo for the latest census (2017)
```{r}
pop_plot <- function(district, n){
  
  plot(district$k1_t ~ district$age, xlim = c(0,100), ylim = c(0,1000), type = "l", xlab = "Age", ylab = "Population", col = "lightcyan3", main = n )
  legend("topright", legend = 1:ncol(district), col = 1:ncol(district), lty = 1, cex = 0.2)
  
  for (i in seq(8,ncol(district), 3)){
    lines(district[ ,i], col = sample(rainbow(ncol(district))))
  }
}

par(mfrow=c(3,2))

pop_plot(d_2017_bayangol, n = "Bayangol")
pop_plot(d_2017_bayanzurkh, n = "Bayazurkh")
pop_plot(d_2017_chingeltei, n = "Chingeltei")
pop_plot(d_2017_hanull, n = "Hanull")
pop_plot(d_2017_songinohairhan, n = "Songinohairhan")
pop_plot(d_2017_suhbaatar, n = "Suhbaatar")

```


plotting year by changes in total population
```{r}
par(mfrow=c(3,2))

plot(d_2017_bayangol$k1_t ~ d_2017_bayangol$age, xlim = c(0,100), ylim = c(0,8000), type = "l", col = "coral4", main  = "Bayangol", xlab = "Age", ylab = "Population")
legend(80, 8000, legend = c("2017", "2016", "2015", "2014", "2011"), col = c("coral4", "coral3", "coral2", "coral1", "coral"), lty=1 , cex = 0.5)

for (i in seq(8,ncol(d_2017_bayangol), 3)){
  
  lines(d_2017_bayangol$total_t, col = "coral4")
  lines(d_2016_bayangol$total_t, col = "coral3", lwd = "0.8")
  lines(d_2015_bayangol$total_t, col = "coral2", lwd = "0.6")
  lines(d_2014_bayangol$total_t, col = "coral1", lwd = "0.4")
  lines(d_2011_bayangol$total_t, col = "coral", lwd = "0.2")
}

plot(d_2017_bayanzurkh$k1_t ~ d_2017_bayanzurkh$age, xlim = c(0,100), ylim = c(0,8000), type = "l", col = "coral4", main  = "Bayanzurkh", xlab = "Age", ylab = "Population")
legend(80, 8000, legend = c("2017", "2016", "2015", "2014", "2011"), col = c("coral4", "coral3", "coral2", "coral1", "coral"), lty=1 , cex = 0.5)
for (i in seq(8,ncol(d_2017_bayanzurkh), 3)){
  
  lines(d_2017_bayanzurkh$total_t, col = "coral4")
  lines(d_2016_bayanzurkh$total_t, col = "coral3", lwd = "0.8")
  lines(d_2015_bayanzurkh$total_t, col = "coral2", lwd = "0.6")
  lines(d_2014_bayanzurkh$total_t, col = "coral1", lwd = "0.4")
  lines(d_2011_bayanzurkh$total_t, col = "coral", lwd = "0.2")
}

plot(d_2017_chingeltei$k1_t ~ d_2017_chingeltei$age, xlim = c(0,100), ylim = c(0,8000), type = "l", col = "coral4", main  = "Chingeltei", xlab = "Age", ylab = "Population")
legend(80, 8000, legend = c("2017", "2016", "2015", "2014", "2011"), col = c("coral4", "coral3", "coral2", "coral1", "coral"), lty=1, cex = 0.5 )
for (i in seq(8,ncol(d_2017_chingeltei), 3)){
  
  lines(d_2017_chingeltei$total_t, col = "coral4")
  lines(d_2016_chingeltei$total_t, col = "coral3", lwd = "0.8")
  lines(d_2015_chingeltei$total_t, col = "coral2", lwd = "0.6")
  lines(d_2014_chingeltei$total_t, col = "coral1", lwd = "0.4")
  lines(d_2011_chingeltei$total_t, col = "coral", lwd = "0.2")
}

plot(d_2017_hanull$k1_t ~ d_2017_hanull$age, xlim = c(0,100), ylim = c(0,8000), type = "l", col = "coral4", main  = "Hanull", xlab = "Age", ylab = "Population")
legend(80, 8000, legend = c("2017", "2016", "2015", "2014", "2011"), col = c("coral4", "coral3", "coral2", "coral1", "coral"), lty=1, cex = 0.5 )
for (i in seq(8,ncol(d_2017_hanull), 3)){
  
  lines(d_2017_hanull$total_t, col = "coral4")
  lines(d_2016_hanull$total_t, col = "coral3", lwd = "0.8")
  lines(d_2015_hanull$total_t, col = "coral2", lwd = "0.6")
  lines(d_2014_hanull$total_t, col = "coral1", lwd = "0.4")
  lines(d_2011_hanull$total_t, col = "coral", lwd = "0.2")
}

plot(d_2017_songinohairhan$k1_t ~ d_2017_songinohairhan$age, xlim = c(0,100), ylim = c(0,8000), type = "l", col = "coral4", main  = "Songinohairhan", xlab = "Age", ylab = "Population")
legend(80, 8000, legend = c("2017", "2016", "2015", "2014", "2011"), col = c("coral4", "coral3", "coral2", "coral1", "coral"), lty=1, cex = 0.5 )
for (i in seq(8,ncol(d_2017_songinohairhan), 3)){
  
  lines(d_2017_songinohairhan$total_t, col = "coral4")
  lines(d_2016_songinohairhan$total_t, col = "coral3", lwd = "0.8")
  lines(d_2015_songinohairhan$total_t, col = "coral2", lwd = "0.6")
  lines(d_2014_songinohairhan$total_t, col = "coral1", lwd = "0.4")
  lines(d_2011_songinohairhan$total_t, col = "coral", lwd = "0.2")
}

plot(d_2017_suhbaatar$k1_t ~ d_2017_suhbaatar$age, xlim = c(0,100), ylim = c(0,8000), type = "l", col = "coral4", main  = "Suhbaatar", xlab = "Age", ylab = "Population")
legend(80, 8000, legend = c("2017", "2016", "2015", "2014", "2011"), col = c("coral4", "coral3", "coral2", "coral1", "coral"), lty=1, cex = 0.5 )
for (i in seq(8,ncol(d_2017_suhbaatar), 3)){
  
  lines(d_2017_suhbaatar$total_t, col = "coral4")
  lines(d_2016_suhbaatar$total_t, col = "coral3", lwd = "0.8")
  lines(d_2015_suhbaatar$total_t, col = "coral2", lwd = "0.6")
  lines(d_2014_suhbaatar$total_t, col = "coral1", lwd = "0.4")
  lines(d_2011_suhbaatar$total_t, col = "coral", lwd = "0.2")
}

```




```{r}
#install/load package to work with raw OSM files
#install.packages("osmar")
library("osmar")

url <- "https://download.geofabrik.de/asia/mongolia-latest.osm.bz2"
file <- "mongolia-latest.osm.bz2"
download.file(url, file)

system("bzip2 -d mongolia-latest.osm.bz2")

src <- osmsource_osmosis(file = "mongolia-latest.osm", osmosis = "osmosis")
ub_bbox <- corner_bbox(106.5926, 47.6785, 107.5861, 48.1213)
ub <- get_osm(ub_bbox, src)


#plot entire object
plot(ub,
     way_args = list(cex = 0.1),
     node_args = list(pch = 20, cex = 0.1)
     )

#just nodes
plot_nodes(ub)
```

I'm not loving the osmar package, lets try some different things
downloaded some landuse data from the interwebs, lets try to plot it

```{r}
#get all the fun spatial packages suggested by visualising spatial data tutorial

x <- c("ggmap", "rgdal", "rgeos", "maptools", "dplyr", "tidyr", "tmap")
#install.packages(x) # warning: uncommenting this may take a number of minutes
lapply(x, library, character.only = TRUE) # load the required packages

landuse <- readOGR(dsn = "./landuse", layer = "landuse")

plot(landuse, xlim = c(106.5509, 107.5444), ylim = c(47.6875, 48.1303)) #coordinates of UB

```
I mean, this doesn't really give us much. Lets try working with some other files I found on the interwebs.

```{r}
buildings <- readOGR(dsn = "./buildings", layer = "hotosm_mng_buildings_polygons")

plot(buildings, xlim = c(106.5509, 107.5444), ylim = c(47.6875, 48.1303)) #coordinates of UB

#let's get a small area in UB to have better look at the resolution

plot(buildings, xlim = c(106.9151, 106.9461), ylim = c(47.9386, 47.9524))

#maybe even smaller

plot(buildings, xlim = c(106.93556, 106.94333), ylim = c(47.94740, 47.95086))


ger <- buildings$building == "ger"

plot(buildings[ger, ], xlim = c(106.5509, 107.5444), ylim = c(47.6875, 48.1303)) #coordinates of UB
par(new = FALSE)
plot(buildings, xlim = c(106.5509, 107.5444), ylim = c(47.6875, 48.1303), col = "red") #why is this not coming up as red? 
```






                                                                                                                                                                                                                                                                                                          