---
title: "From questions to composites"
author: "Natalia Fedorova"
date: "8/14/2019"
output: html_document
---
This document details how individual questions in the "Constructing Permanence" Survey become composite measures used in the analysis

Here we simulate possible question answers, and use this simulated data to create composites that will them be analysized and matched with the ABM

The survey questions

See files x and y for questions in hasha and household surveys respectively


Variables of interest

data sim set up
```{r}
N_hh <- 100



```

Capital

The capital variable will be made from questions in Section C

think about whether education should just be included in capital (because it will correlate) or if we want that as its own variable?

# c4: change to income since coming to UB, if relevant
# what to extract: increase, decrease, no change
# this question is actually not for capital, but for capital accumulation (informas parameters of ABM)

#c6 part 2 (for strategy assessment)
assets_outside_UB <- sample(0:100, N_hh, replace = TRUE)
assets_outside_UB <- assets_outside_UB/total_assets

```{r}
# c1: who contributes (name, occupation, length of employment)
# what to extract: number of earners

n_earners <- sample(0:6, N_hh, replace = TRUE)

# c2: sources of income
# what to extract

# c3: proportion of income saved
# what to extract: answer as is, 0 = nothing, 1 = <10, 2 = <25, 3 = 25-50, 4 = >50, NaN is don't know (didn't answer should be something else)

saving_prop <- sample(c(0, 1, 2, 3, 4, NaN), N_hh, replace = TRUE)

# c5: loans
# what to extract: total number of different loans

loans <- sample(0:6, N_hh, replace = TRUE)

# c6: assets
# what to extract: this is a very informative question,  1: total number of things owned, 2: proportions of things owned in and out of UB (used in strategy assessment)
#part 1 (might also want to rank these assets)
total_assets <- sample(0:300, N_hh, replace = TRUE)

# f6: value of hasha (if owned)
# what to extract: actual value of hasha (range)

hasha_value <- sample(c(1:6, NaN), N_hh, replace = TRUE)

# ga or gb
# what to extract: does household own hasha (yes/no)

hasha_own <- sample(0:1, N_hh, replace = TRUE)

# ha or hb
# what to extrat: does household own dwelling (yes/no)

dwelling_own <- sample(0:1, N_hh, replace = TRUE)


# constructing "capital"



```

Social Capital

Household Composition

Urban experience

Intended stay

Outcome variables

Investment

House type

Residence length?




