---
title: "From questions to composites"
author: "Natalia Fedorova"
date: "8/14/2019"
output: html_document
---
This document details how individual questions in the "Constructing Permanence" Survey become composite measures used in the analysis

Here we simulate possible question answers, and use this simulated data to create composites that will them be analysized and matched with the ABM

The survey questions

See files x and y for questions in hasha and household surveys respectively


Variables of interest

data sim set up
```{r}
N_hh <- 100

# NaN means don't know
# NA means there is no answer, question was left blank 
# doesn't apply generally not coded
# yes/no questions turned to 1/0 respectively 
# categorical answers given values from 1:max
```

Capital

think about whether education should just be included in capital (because it will correlate) or if we want that as its own variable?

# c4: change to income since coming to UB, if relevant
# what to extract: increase, decrease, no change
# this question is actually not for capital, but for capital accumulation (informas parameters of ABM)

#c6 part 2 (for strategy assessment)
assets_outside_UB <- sample(0:100, N_hh, replace = TRUE)
assets_outside_UB <- assets_outside_UB/total_assets

```{r}
# c1: who contributes (name, occupation, length of employment)
# what to extract: number of earners

n_earners <- sample(0:6, N_hh, replace = TRUE)

# c2: sources of income
# what to extract

# c3: proportion of income saved
# what to extract: answer as is, 0 = nothing, 1 = <10, 2 = <25, 3 = 25-50, 4 = >50, NaN is don't know (didn't answer should be something else)

saving_prop <- sample(c(0, 1, 2, 3, 4, NaN), N_hh, replace = TRUE)

# c5: loans
# what to extract: total number of different loans

loans <- sample(0:6, N_hh, replace = TRUE)

# c6: assets
# what to extract: this is a very informative question,  1: total number of things owned, 2: proportions of things owned in and out of UB (used in strategy assessment)
#part 1 (might also want to rank these assets)
total_assets <- sample(0:300, N_hh, replace = TRUE)

# fa5: economic situation at hasha move in
# what to extract: category of worse, same, better

capital_at_hasha_move_in <- sample(1:3, N_hh, replace = TRUE)

# fa6: value of hasha (if owned)
# what to extract: actual value of hasha (range)

hasha_value <- sample(c(1:6, NaN), N_hh, replace = TRUE)

# fb4: economic situation at move in to dwelling
#what to extract: category of worse, same, better, doesn't apply

capital_at_dwelling_move_in <- sample(c(1:3, NaN), N_hh, replace = TRUE)

# ga or gb
# what to extract: does household own hasha (yes/no)
# this is also for ownership 

hasha_own <- sample(0:1, N_hh, replace = TRUE)

# ha or hb
# what to extrat: does household own dwelling (yes/no)
# this is also for ownership

dwelling_own <- sample(0:1, N_hh, replace = TRUE)




# constructing "capital"



```

Social Capital

Measured in this survey as presence of family in UB (of anyone in the household). Family is extremely important in Ulaanbaatar, both for incomers and for long term residents.

```{r}
# b1: n of related households
# what to extract: category of how many related families in UB

n_fam <- sample(c(1:4, NaN), N_hh, replace = TRUE)

# b2: relatives that live walking distance
# what to extract: yes, no, don't know, doesn't apply

fam_walk <- sample(c(1:2, NaN), N_hh, replace = TRUE)

# b3: closeness to said family
# what to extract: category - not close, medium, close

fam_close <- sample(1:3, N_hh, replace = TRUE)

# ga2: who did you aquire hasha from
# what to extract: yes/no acquired from family (could also use the friend component of this question)

hasha_from_fam <- rbinom(N_hh, 1, prob = 0.5)

# gb1: who owns the hasha
# what to extract: yes/no family owns the hasha

hasha_fam_own <- rbinom(N_hh, 1, prob = 0.5)

# gb4: who did you find out about this hasha from
# what to extract: yes/no from family

hasha_fam_recom <- rbinom(N_hh, 1, prob = 0.5)

# ha2: who did you acquir the dwelling from
# what to extract: yes/no from family

dwelling_from_fam <- rbinom(N_hh, 1, prob = 0.5)

# ha3 question about how you acquired it? also in the g section for acquiring hasha

# hb1: who owns the dwelling
# what to extract: yes/no from family 

dwelling_fam_own <- rbinom(N_hh, 1, prob = 0.5)

# hb5: how did you find out about the dwelling?
# what to extract: yes/no from family

dwelling_fam_recom <- rbinom(N_hh, 1, prob = 0.5)

# ia4: who helped you build the dwelling
# what to extract: yes/no family did

dwelling_fam_help <- rbinom(N_hh, 1, prob = 0.5)

# ia6: who have  you helped build a dwelling
# what to extract: yes/no family

built_fam_dwelling <- rbinom(N_hh, 1, prob = 0.5)

# ib1: who built the dwelling you are living in
# what to extract: yes/no family built it

dwelling_fam_built <- rbinom(N_hh, 1, prob = 0.5)

```

Household Composition

```{r}
# a2: total number of adults
# what to extract: as is, total number of adults

hh_adults <- sample(1:10, N_hh, replace = TRUE)

# a3: total number of children
# what to extract: as is, total number of children

hh_children <- sample(1:10, N_hh, replace = TRUE)   #these should actually be drawn as whole numbers from a distribution


# aside from this very basica profile, need to construct the different categories of household (single, couple, breeding pair, bp with young children, bp with old children, bp and adult children, bp and other dependents, retirees), bearing in mind that families might not tightly fit in either of these categories. In any case, to construct these we use answer from Section A: the household census




```



Urban experience?



Intended stay

```{r}
# e1a or a1b: do you intend to stay in UB
# what to extract: yes/no 

intend_stay <- rbinom(N_hh, 1, prob = 0.5)

# E2 for intend to stay, for how long?
# what to extract: category of length of stay

intend_stay_length <- sample(1:5, N_hh, replace = TRUE)

# E2 for don't intend to stay, when do you plan to leave?
# what to extract: category of when you plan to leave

intend_leave_length <- sample(1:5, N_hh, replace = TRUE)

# e3 for stay, why?
# what to extract: cateogry of why they intend to stay

intend_stay_reason <- sample(1:6, N_hh, replace = TRUE)

# e3 for leave, why?
# what to extract: cateogry of why they intend to leave

intend_leave_reason <- sample(1:6, N_hh, replace = TRUE)


# composite measure for intend_stay


```

Outcome variables

Investment

```{r}
# fa3: does hasha require investment in money/time?
# what to extract: yes/no/don't know

hasha_maintenance <- sample(c(1:2, NaN), N_hh, replace = TRUE)

# fa4: any big repairs on hasha?
# what to extract: yes/no/don't know

hasha_repairs <- sample(c(1:2, NaN), N_hh, replace = TRUE)

# fb2: time/maintenance on dwelling?
# what to extract: yes/no/ don't know 

dwelling_maintenance <- sample(c(1:2, NaN), N_hh, replace = TRUE)

# fb3: any big repairs on dwelling?
# what to extract: yes/no/don't know

hasha_repairs <- sample(c(1:2, NaN), N_hh, replace = TRUE)

# ga3: how did you acquire the hasha? 
# what to extract: how to include it

# ga4: when you purchased the hasha, how much was it?
# what to extract: category of cost

hasha_purchase_cost <- sample(c(1:6, NaN),  N_hh, replace = TRUE)

# for hh that don't own the hasha

# gb2: do you pay or provide a service to stay on this hasha?
# what to extract: yes/no

service_for_hasha <- rbinom(N_hh, 1, prob = 0.5)

# gb3: did you pay a one time fee to stay on the hasha
# what to extract: yes/no

hasha_fee <- rbinom(N_hh, 1, prob = 0.5)

# gb5: what have you built on this hasha
# what to extract: category of thing built

hasha_invst_built <- sample(0:3, N_hh, replace = TRUE)

# dwelling investment

# again ha3 should probably be included - how did you acquire it

# for those who do not own the dwelling

# hb2: how much do you pay to stay in this dwelling per month
# what to extract: number amount in MNT

dwelling_rent <- rnorm(N_hh, mean = 600000, sd = 300000)

# hb3: did you pay a one time fee to stay at this dwelling
# what to extract: yes/no

dwelling_fee <- rbinom(N_hh, 1, prob = 0.5)

# hb4: have you provided some service to the owner
# what to extract: yes/no

service_for_dwelling <- rbinom(N_hh, 1, prob = 0.5)

# for households that built their own dwelling

# ia2: how long did it take to construct it
# what to extract: categories of length

dwelling_construct_time <- sample(1:4, N_hh, replace = TRUE)

# ia3: total cost to construct it
# what to extract: category of cost

dwelling_construct_cost <- sample(1:6, N_hh, replace = TRUE)

# ia5: how many people built it
# what to extract: as is, number

dwelling_construct_manpower <- sample(1:20, N_hh, replace = TRUE)

# for hh that didnt build their own dwelling

# ib2: have you sig. altered the dwelling
# what to extract: yes/no

dwelling_alter <- rbinom(N_hh, 1, prob = 0.5)


# Now, investment parameters based on ownership situation 


```

House type

```{r}
# answer should be in d5 max, column C - this should record the latest address
# but it would be best to check this with Hasha survey, matching structure in section D with residents, and with total residents in hh survey A2, to double check

# d5 max, column C: type of dwelling
# what to extract: category type of dwelling ger, bashin, apt

dwelling_type <- sample(1:3, N_hh, replace = TRUE)

# also interested in the macro property of the ger districts, so want to count up to get proportions of gers and bashins (and apt, which should never appear)

n_ger <- length(dwelling_type[which(dwelling_type == 1)])
n_bashin <- length(dwelling_type[which(dwelling_type == 2)])
n_apt <- length(dwelling_type[which(dwelling_type == 3)])

```

Residence length total

```{r}
# d51, column b: residence start year
# what to extract: as is, start year

ub_start_year <- sample(1990:2019, N_hh, replace = TRUE)

```

Residence length plot

```{r}
# fa1: year hh started living on current hasha
# what to extract: as is, star tyear

hasha_start_year <- ub_start_year <- sample(1990:2019, N_hh, replace = TRUE)

# this should be possible to check against d5max, column b, as that should be the current plot

```



Pilot data

Parameters/Priors to input

number of initial movements in UB before current hasha (for squatter dynamic)
capital accumulation (does economic situation usually improve, or not, or halfhalf), for abm simulation



